---
title: "Lab 10 - Grading the professor, Pt. 2"
author: "Heather Hawkins"
date: "04-10-23"
output: github_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(tidymodels)
library(openintro)
```

### Exercise 1

```{r chunk}
?evals

m_bty <- lm(score ~ bty_avg, data = evals)
summary(m_bty)
```
y = 3.88 + 0.066(bty_avg)

The r^2 is 0.035 and the adjusted r^2 is 0.033

### Exercise 2

```{r codechunk2}
m_bty_gen <- lm(score ~ bty_avg + gender, data = evals)
summary(m_bty_gen)
```
y = 3.74 + 0.066(bty_avg) + 0.17(gender)

The r^2 is 0.059 and the adjusted r^2 is 0.055

### Exercise 3

The intercept is the average score for female professors with an average beauty rating of 0
The slope of bty_avg is the change in score for a one-unit increase in beauty rating, holding gender constant (meaning that the score raises 0.07 for each increase in beauty).The slope of gender shows us that male professors have a score that is 0.17 higher than female professors. 


### Exercise 4

The adjusted R2 value for m_bty_gen gives the percentage of variability in score that is explained by the model. Meaning that m_bty_gen explains (5.9%) of the variance in the score. 


### Exercise 5

y = 3.91 + 0.066(bty_avg)


### Exercise 6

Male professors tend to have a higher course evaluation score.


### Exercise 7

```{r chunk4}
m_bty_gen_int <- lm(score ~ bty_avg * gender, data = evals)
summary(m_bty_gen_int)
```

The relationship between beauty and evaluation score is stronger for female professors than for male professors.

### Exercise 8

The adjusted R2 for m_bty_gen is slightly higher than that for m_bty, this means that gender provides some additional explanatory power beyond beauty rating alone. 


### Exercise 9

The slope for bty_avg is similar between the two models, the addition of gender did not substantially change the relationship between beauty rating and evaluation score.

### Exercise 10


```{r intired}
m_bty_rank <- lm(score ~ bty_avg + rank, data = evals)
summary(m_bty_rank)
```
y = 3.98+ 0.68(bty_avg) + -0.13(tenured) + -.16(tenure_track)

The intercept is the average score for assistant professors with an average beauty rating of 0.

The slope of bty_avg, holding rank constant, states that with a bty increase of 1, score would increase by 0.68

The slope of tenured states that tenured professors have scores decreased by -0.13

The slope of tenure_track states that tenure track professors have scores decreased by -0.16

### Exercise 11

Based on the given variables, we would expect ethnicity to be the worst predictor of evaluation scores. This is because ethnicity is not related to the professor's ability to teach or students' evaluation of the course. 


### Exercise 12

To confirm this, we can fit a simple linear regression model with evaluation score as the response variable and ethnicity as the predictor variable:

```{r chunk5}
m_eth <- lm(score ~ ethnicity, data = evals)
summary(m_eth)
```
Ethnicity doesnt seem to influence scores at all. 

### Exercise 13

If we are already including cls_perc_eval and cls_students in the full model, we should not include cls_did_eval as an additional predictor. This is because cls_did_eval is highly correlated with cls_perc_eval (that they are basically the same thing).

### Exercise 14


```{r code}
full_model <- lm(score ~ rank + ethnicity + gender + language + age + cls_perc_eval + 
                  cls_students + cls_level + cls_profs + cls_credits + bty_avg, data = evals)
summary(full_model)
```

### Exercise 15


```{r h}
linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg + cls_perc_eval+ cls_students+ rank, data = evals) %>%
  tidy()

summary(lm(score ~ bty_avg + cls_perc_eval+ cls_students+ rank, data = evals))
```
The final model includes the following variables: cls_perc_eval, cls_students, bty_avg, and rank.

The linear model for predicting score based on the final model is:

y = -2.29 + 0.04(cls_perc_eval) + 0.05(cs_students) + 0.13 (bty_avg) - 0.07(rank)



### Exercise 16

One numerical predictor in the final model is bty_avg, which represents the average beauty rating of the professor. The slope coefficient of 0.13 indicates that a 1 unit increase in bty_avg is associated with a 0.13-point increase in evaluation score.

One categorical predictor in the final model is rank, which represents the academic rank of the professor (1 for assistant professor, 2 for associate professor, and 3 for full professor). The slope coefficient of -0.07 indicates that being a full professor is associated with a 0.07-point decrease in evaluation score compared to being an assistant professor.

### Exercise 17

A high-scoring professor and course at the University of Texas at Austin would have the following characteristics:

Higher values of cls_perc_eval and cls_students (i.e., higher course evaluations and more students in the course)
Higher values of bty_avg (i.e., a higher average beauty rating for the professor)
Lower rank (i.e., being an assistant or associate professor rather than a full professor)

### Exercise 18

Would you be comfortable generalizing your conclusions to apply to professors generally (at any university)? Why or why not?

Not at all.The model was built using data from the University of Texas at Austin and is not representative of other universities. There may be other variables that are important predictors of evaluation scores at other universities that weren't included in this model. Thus, the model would need to be reevaluated. 
...


